Predicting Which States are Most Interested in the term *China Virus* Based off Identity Politics, Demography and COVID-19 Statistics 

### 2020-05-05 Final-Draft.Rmd
changes

pred_FL_RM <- data.frame(y_new = pred_FL[-1])

@@

pred_FL_NR <- data.frame(y_new = pred_FL[-1])

@@

pred_FL_3 <- data.frame(y_new = pred_FL[-1])

@@

pred_FL_complex <- data.frame(y_new = pred_FL[-1])

@@

summary(pred_FL_complex)
```

```{r}

actual_FL_pred<-Finaldata %>% select(c(State, ChinaVirusInterest)) %>% filter(State =="FL") %>% summarise(mean=mean(ChinaVirusInterest))

actual_FL_pred
```

>>>>

pred_FL_RM <- data.frame(y_new = pred_FL_RM[-1])

@@

pred_FL_NR <- data.frame(y_new = pred_FL_NR[-1])

@@

pred_FL_3 <- data.frame(y_new = pred_FL_3[-1])

@@

pred_FL_complex <- data.frame(y_new = pred_FL_complex[-1])

@@

complex<-summary(pred_FL_complex)
```

```{r}
actual_FL_pred<-Finaldata %>% select(c(State, ChinaVirusInterest)) %>% filter(State =="FL") %>% summarise(mean=mean(ChinaVirusInterest))
actual_FL_pred
```

```{r}
modelevalFL<-read_csv("MODELEVAL.csv")
```
